\vspace{-3em} \includegraphics[width=.1\textwidth]{Figures/logo.png} \\ \includegraphics[width=4cm]{Figures/logotext.png} \\

### 2014-11-03 report/article_4.tex
gmap
new report figure
rm unneeded files; add some comments

I analysed the {\bf London house prices} dataset is several innovative
ways. Firstly \emph{fractal context} shows how house sales within an
arbitrary area relate to those if neighbouring districs, up and down
the postcode hierarchy. Secondly, I fit \emph{ARIMA models} to
forecast an area's price trend into the future, with an eye to
suggesting profitable investments. Finally, these and other metrics
were combined into an \emph{investment grade} for a given postcode
area. Together this set of analyses forms the basis of \logo, a
startup aimed at \emph{democratising real estate investment}, offering
individuals and businesses quantitative property area insights for
data-driven investment decisions.

@@

\vspace{-1em}
\section*{Analyses}

@@

\setlength{\intextsep}{0em}
\begin{wrapfigure}{R}{.45\textwidth}
%\vspace{-1em}
\centering
\includegraphics[width=.44\textwidth]{Figures/grading.png}
\vspace{-1em}
\caption{ Quantile transformation for investment grading
  (AAA rated sectors in \emph{navy}).}
\vspace{.5em}
\end{wrapfigure}

@@

%----------------------------------------------------------------------------------------
%	METHODS
%----------------------------------------------------------------------------------------
\clearpage
\section*{Value generation}

@@

\subsection*{2. Direct-to-consumer demo application}
\logo \hspace{.1em} would release both a {\bf web service} and associated
{\bf mobiles and tablet applications}. These would offer limited analysis and
visualisation without any fee, with collected user data and feedback helping to
validate the business model and develop our software.

@@

\clearpage

@@

In this report I've given a brief overview my attempts to elute maximal
insight from a single large dataset through the data science techniques of
visualisation and quantitative modelling. Together they form a
cohesive narrative of investigative analysis into a single exemplar
postcode, and discovery of the potential investment returns
therein.

These analyses have to potential to generate valuable insights for a range of
customer segments:
\begin{itemize}

@@

\vspace{2em}
\begin{figure}[h!]
\begin{center}
\includegraphics[width=.15\textwidth]{Figures/logo.png} \\
\includegraphics[scale=.12]{Figures/logotext.png} \\
\caption*{ {\sf Democratising real estate investment}}
\end{center}
\end{figure}

>>>>

I analysed the {\bf London house prices} dataset in several innovative
ways. Firstly \emph{fractal context} shows how house sales within an
arbitrary area relate to those if neighbouring districs, up and down
the postcode hierarchy. Secondly, I fit \emph{ARIMA models} to
forecast an area's price trend into the future, with an eye to
suggesting profitable investments. Finally, these and other metrics
were combined into an \emph{investment grade} for a given postcode
area. Together this set of analyses forms the basis of \logo, a
startup aimed at \emph{democratising real estate investment}, offering
individuals and businesses quantitative property area insights to enable
data-driven investment decisions.

@@

\vspace{-1em}
\section*{Section A: Analyses}

@@

\setlength{\intextsep}{0em}
\begin{wrapfigure}{R}{.45\textwidth}
\vspace{.5em}
\centering
\includegraphics[width=.44\textwidth]{inkscape/grading_2.png}
\vspace{-1em}
\caption{ Quantile transformation for investment grading
  (AAA rated sectors in \emph{navy}).}
\vspace{.5em}
\end{wrapfigure}

@@

%----------------------------------------------------------------------------------------
%	METHODS
%----------------------------------------------------------------------------------------
\clearpage
\section*{Section B: Value generation}

@@

\begin{figure}[h]
\vspace{1.5em}
\centering
\includegraphics[width=.85\textwidth]{Figures/gmapScreenshot.png}
\vspace{.5em}
\caption{ A basic embeddable web app built with the Google Maps API
  (viewable at \href{http://blm.io/datarea}{blm.io/datarea}). }
\end{figure}

\subsection*{2. Direct-to-consumer demo application}

\logo \hspace{.1em} would release both a {\bf web service} and associated
{\bf mobiles and tablet applications}. These would offer limited analysis and
visualisation without any fee, with collected user data and feedback helping to
validate the business model and develop our software.

@@

@@

\begin{wrapfigure}[10]{r}{.3\textwidth}
\vspace{2em}
\centering
\includegraphics[width=.2\textwidth]{Figures/logo.png}
\includegraphics[width=.2\textwidth]{Figures/logotext.png}
%\caption*{ {\sf Democratising real estate investment}}
\caption{ Logo design. }
%\vspace{-4em}
\end{wrapfigure}

In this report I've given a brief overview my attempts to elute
maximal insight from a single large dataset through visualisations and
quantitative modelling. Together these form a cohesive narrative of
investigative analysis into a single exemplar postcode, and discovery
of the potential investment returns therein.

These analyses have the potential to generate valuable insights for a range of
customer segments:
\begin{itemize}

@@

%\vspace{2em}
% \begin{figure}[h!]
% \begin{center}
% \includegraphics[width=.15\textwidth]{Figures/logo.png} \\
% \includegraphics[scale=.11]{Figures/logotext.png} \\
% \caption*{ {\sf Democratising real estate investment}}
% \end{center}
% \end{figure}
